Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-11 paper/paper.tex
edits

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight{}, and \smonkey\ whereas \hermes performs
worse when compared to the other engines.
\Fix{This happens because \hermes
still has many unsupported features, such as Proxy, Promisse, and XXX.}
Moreover, one can also note that \chakra\ also a low passing ratio
in this test suite and the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. As aforementioned,
it is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

>>>>

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight{}, and \smonkey\ whereas \hermes performs
worse when compared to the other engines.
\Fix{This happens because \hermes
still has many unsupported features, such as Proxy, Promisse, and Async.}
Moreover, one can also note that \chakra\ also a low passing ratio
in this test suite and the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. As aforementioned,
it is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.
